### 2017-01-30 Hhh/Hhh.tex
Adding some more stuff

The discovery of the 125 GeV Higgs boson by the ATLAS and CMS collaborations in 2012 \cite{HDiscoveryAtlas,HDiscoveryCMS} has opened up
new possibilities for probing the Higgs sector beyond the Standard Model. As discussed in chapter \ref{chap:theory}, in some \ac{MSSM} scenarios, and some more
generic type-II 2HDM's, a heavy neutral Higgs boson H can decay to a pair of 125 GeV Higgs bosons for low values
of \tanb, probing a region of phase space not yet excluded by the stringent existing limits. In regions where
the decay \Htohh is enhanced, the \AtoZh decay also has a large branching ratio, indicating the usefulness
of both channels for probing the low-\tanb~region. The $b\bar{b}$\tautau final state is chosen for the combination
of the large $h(125) \rightarrow b\bar{b}$ branching ratio and the cleaner \htotautau final state.

>>>>

The discovery of the 125 GeV Higgs boson by the ATLAS and CMS collaborations in 2012 \cite{HDiscoveryATLAS,HDiscoveryCMS} has opened up
new possibilities for probing the Higgs sector beyond the Standard Model. As discussed in chapter \ref{chap:theory}, in some \ac{MSSM} scenarios, and some more
generic type-II 2HDM's, a heavy neutral Higgs boson H can decay to a pair of 125 GeV Higgs bosons for low values
of \tanb, probing a region of phase space not yet excluded by the stringent existing limits. In regions where
the decay \Htohh is enhanced, the \AtoZh decay also has a large branching ratio, indicating the usefulness
of both channels for probing the low-\tanb~region. The $b\bar{b}$\tautau final state is chosen for the combination
of the large $h(125) \rightarrow b\bar{b}$ branching ratio and the cleaner \htotautau final state.

### 2017-01-30 Theory/Theory.tex
Adding some more stuff

\chapter{Introduction and theory}
\label{chap:theory}

\section{The standard model of particle physics}
\label{sec:theory_sm}

@@

On the fourth of July 2012 the ATLAS and CMS collaborations
announced the discovery of a boson with a mass of around 125 GeV \cite{HDiscoveryATLAS,HDiscoveryCMS}.
The observations were based on excesses in the search for $\PHiggslight\rightarrow\gamma\gamma$ and $\PHiggslight\rightarrow \PZ\PZ$.
More data were collected and analysed during the remainder of 2012, and subsequent studies 
grew the confidence in this boson being compatible with the standard model Higgs boson. The ATLAS and CMS combined
mass measurement using the full dataset of Run 1 of the \ac{LHC} 
found \mh = $125.09 \pm 0.21 \text{ (stat) } \pm 0.11 \text{ (syst) }$ GeV \cite{MassComb}.
The combined ATLAS and CMS production- and decay rate measurement, also using the full dataset of \ac{LHC} Run 1,
shows very good agreement with the \ac{SM} predictions \cite{CouplComb}. Some discrepancies
with the \ac{SM} predicition do remain, and so the measurements of \ac{SM} Higgs boson
properties are certainly not finished yet.

@@

During Run 2

\section{Beyond the standard model}
\label{sec:theory_BSM}
The \ac{SM} has been successfully tested to high accuraccy. However,
some issues remain that cannot be addressed by the \ac{SM} alone.
For example BLAH BLAH

Therefore \acf{BSM} theories have been developed
that aim to cover some of these issues. One of the most
popular of such theories is \acf{SUSY} \cite{SUSY-primer}, which postulates
that there is a symmetry between bosons and fermions. Every fermionic
\ac{SM} particle has a bosonic superpartner (named `s'+name of fermion, e.g.
sbottom, selectron,...), and every bosonic \ac{SM} particle
has a fermionic superpartner (named boson name + `ino', e.g. higgsino, Wino,...).

If this symmetry were unbroken the \ac{SUSY} particles must
have the same mass as their \ac{SM} partners. However, we know that
this is not the case as such particles would have been detected a long time ago. The 
only possibility is then that \ac{SUSY} is a broken symmetry and the superpartners
are heavier than their \ac{SM} equivalents.

\subsection{The Higgs sector of the MSSM}
\label{sec:theory_MSSM_H}
At least two Higgs doublets are required in the
Higgs sector of the MSSM due to the supersymmetric
background of the theory \cite{MSSM-carena-haber}. Two complex Higgs doublets are added,
\begin{equation}\label{eqn:mssm_higgsdoublets}
\phi_d = \begin{pmatrix} \phi_d^0 \\
\phi_d^- \end{pmatrix} \text{ and } \phi_u = \begin{pmatrix} \phi_u^+ \\
\phi_u^0 \end{pmatrix}
\end{equation}
Note that $\phi_d^0$ couples exclusively to down-type fermions, and $\phi_u^0$ couples
exclusively to up-type fermions.
This leads to potential terms in the MSSM Lagrangian of the form:
\begin{equation}\label{eqn:mssm_lagrangian_potential}
V = \mu(\phi_u^+\phi_d^- - \phi_u^0\phi_d^0),
\end{equation}
with $\mu$ a mass parameter, equivalent to the \ac{SM} Higgs mass parameter.
This provides electroweak symmetry breaking as in the \ac{SM} case and
minimising this potential gives,
\begin{equation}\label{eqn:mssm_minimpot}
\langle 0|\phi_d| 0 \rangle = \begin{pmatrix}v_d\\
0 \end{pmatrix} \text{ and} \langle 0 |\phi_d|\rangle 0 = \begin{pmatrix} 0\\
v_u \end{pmatrix}
\end{equation}
Using this we define
\begin{equation}\label{eqn:tanb_def}
\tan{\beta} \equiv \frac{v_u}{v_d}
\end{equation}
Of the eight degrees of freedom due to the introduction of two complex
doublets, three become longitudinal states of the $\PW^{\pm}$ and \PZ bosons.
The remaining 5 degrees of freedom lead to five physical Higgs bosons, a charged
Higgs boson pair $\PHiggs^{\pm}$, the neutral pseudoscalar \PHiggsps
and the neutral scalars h and H. These are defined in terms
of \tanb~and a mixing angle $\alpha$ which arises from diagonalising
the neutral scalar Higgs squared-mass matrix, see equation \ref{eqn:treelevel_mass}. The five bosons become:
\begin{align}\label{eqn:MSSMHiggsMixing}
&\PHiggs^+ = \phi_u^+\cos{\beta} + \phi_d^{-\dagger}\sin{\beta},\\
&\PHiggs^- = \phi_u^{+\dagger}\cos{\beta} + \phi_d^{-}\sin{\beta},\\
&\PHiggsps = \sqrt{2}(\text{Im}\phi_d^0\sin{\beta} + \text{Im}\phi_u^0\cos{\beta}),\\
&\PHiggslight = -(\sqrt{2}\text{Re}\phi_d^0 - v_d)\sin{\alpha} + (\sqrt{s}\text{Re}\phi+u^0 -v_u)\cos{\alpha}\\
&\PHiggs = (\sqrt{2}\text{Re}\phi_d^0-v_d)\cos{\alpha}+(\sqrt{2}\text{Re}\phi_u^0-v_u)\sin{\alpha}
\end{align}
As the self-interactions of the Higgs fields are not independent parameters
but are functions of the electroweak gauge coupling constants, at tree
level the MSSM Higgs sector parameters are determined by two free parameters, \tanb~and
one of the Higgs boson masses, conventionally chosen as \mA.
Using this the masses of the five Higgs states are found as:
\begin{equation}\label{mssm_chargedhigss_mass}
m_{\PHiggs^{\pm}}^2 = m_{\PHiggsps}^2+m_{\PW}^2,
\end{equation}
while the neutral scalar \PHiggslight and \PHiggs are eigenstates of the tree-level
squared-mass matrix:
\begin{equation}\label{eqn:treelevel_mass}
\mathcal{M}_{\text{tree}}^2 = \begin{pmatrix} 
m_{A}^2\sin{\beta}^2 + m_{Z}^2\cos{\beta}^2 & -(m_{A}^2+m_{Z}^2)\sin{\beta}\cos{\beta}\\
-(m_{A}^2+m_{Z}^2)\sin{\beta}\cos{\beta} & m_{A}^2\cos{\beta}^2+m_{Z}^2\sin{\beta}^2 \end{pmatrix}.
\end{equation}
This leads to the masses of \PHiggslight and \PHiggs as eigenvalue of $\mathcal{M}_{\text{tree}}^2$,
\begin{equation}\label{eqn:scalarmass}
m_{\PHiggs,\PHiggslight}^2 = \frac{1}{2}(m_{A}^2+m_{Z}^2 \pm \sqrt{(m_A^2+m_Z^2)^2-4m_Z^2m_A^2\cos{2\beta}^2}).
\end{equation}
A consequence of this is a tree-level upper bound to the mass of the light Higgs
boson,
\begin{equation}\label{eqn:mh_upper}
m_{h} \leq m_{Z},
\end{equation}
and a constraing on $\alpha$,
\begin{equation}\label{eqn:alpha_constraint}
\cos{(\beta-\alpha)}^2 = \frac{m_h^2(m_Z^2-m_h^2)}{m_A^2(m_H^2-m_h^2)}.
\end{equation}

@@

In Run-2 of the \ac{LHC} searches for \AHtotautau, setting more stringent limits than those shown in \ref{fig:bsm_summary},
have been performed in \ac{CMS}. The results of these searches will be presented in chapter \ref{chap:mssm}. Other searches
for heavy Higgs bosons with decays to other final states are also in progress as the Run-2 data keep
amassing.

>>>>

\chapter{Theory and motivation}
\label{chap:theory}
To understand and motivate the searches presented in chapters 
\ref{chap:hhh} and \ref{chap:mssm} it is important
to understand the theory and phenomenology behind them. 
This chapter describes the \acl{SM} of particle physics, the
motivations for \acl{SUSY} and the phenomenology of Higgs
sectors beyond the \acl{SM}.

\section{The \acl{SM} of particle physics}
\label{sec:theory_sm}
The \ac{SM} of particle physics is a theory that describes the weak and strong
nuclear forces, plus the \ac{EM} force, and the interaction of those forces
with particles. The \ac{SM} is a \ac{QFT} in which matter particles
are represented by spin-$\frac{1}{2}$ fermions, with the forces represented
by spin-1 bosons.

\subsection{Fundamental particles and forces}
\label{sec:theory_sm_particles}
In the \ac{SM} there are twelve fundamental fermions, six quarks and
six leptons. The quarks interact via both strong nuclear force and the 
electroweak force, while
the leptons only interact via the electoweak force.
Each of the fermions has a corresponding antiparticle
with opposite quantum numbers. The quarks and leptons
are divided into three generations. The particles from different
generations have similar properties, apart from the mass which increases
for each generation. The quarks and leptons are summarised in 
table \ref{tab:theory_fermions}.

\begin{table}[htp]
\begin{center}
\caption{The fundamental fermions}
\begin{tabular}{@{}llll@{}}
\toprule
 & \textbf{1st generation} & \textbf{2nd generation} & \textbf{3d generation}\\
\midrule
\textbf{Quarks} & & & \\
\midrule
Charge: +$\frac{2}{3}$& up (\Pup)  & charm (\Pcharm) & top (\Ptop) \\
Charge: -$\frac{1}{3}$& down (\Pdown) & strange (\Pstrange) & bottom (\Pbottom) \\
\midrule
\textbf{Leptons} & & & \\
\midrule
Charge: -1 & electron (\Pe) & muon (\Pgm) & tau (\Pgt) \\
Charge: 0  & electron neutrino ($\Pgn_{\Pe}$) & muon neutrino ($\Pgn_{\Pgm}$) & tau neutrino ($\Pgn_{\Pgt}$)\\
\bottomrule
\end{tabular}
\label{tab:theory_fermions}
\end{center}
\end{table}

The forces in the \ac{SM} are mediated by spin-1 bosons: The gluon (\Pgluon),
which carries the strong force, the photon (\Pphoton) as the
electromagnetic force carrier, and the $\PW^{\pm}$ and \PZ bosons, the
force carriers of the weak nuclear force.

The particles that interact via the strong force carry colour charge (red, green, or blue),
as do their mediators, the gluons. The interactions in the \ac{QFT} of the
strong force, called \ac{QCD}, are governed by an SU(3) (colour) symmetry.
%There are 8 gluons due to the SU(3) symmetry, colour octet and a colour singlet, but
%if there was a colour singlet it should occur as a free particle while it does not.
%See chapter 285 of griffiths
The quarks are never observed in isolation but always in bound
hadron states, which is referred to as confinement. Due to asymptotic
freedom \cite{asympt-I,asympt-II}, the strong coupling strength decreases at 
high energy (short distances). More detailed introductions to \ac{QCD} can 
be found in ref. \cite{griffiths}.

Particles that carry electric charge interact via the 
electromagnetic force, summarised in by the rules of \ac{QED}. 
The weak interaction, governed by weak isospin transformations,
only couples to the left-handed part of the fermion states. In 
general a fermion state can be decomposed into its left- and right-handed parts
\begin{equation}\label{eqn:leftright}
\chi=\psi_R+\psi_L,
\end{equation}
and only $\psi_L$ will interact via the weak force. Handedness and
helicity have the same eigenstates for massless particles, and as
such neutrinos, which are massless in the \ac{SM}, must all be left-handed.
The observation of neutrino flavour oscillations since the formulation of
the \ac{SM} implies that neutrinos do have a small but finite mass
and so there must be right-handed neutrinos in the \ac{SM}. This is
not discussed further here ADD REFERENCE.
The weak isospin acts on doublets of left-handed lepton pairs, while
the right-handed leptons transform as singlet states. This works similarly
for the quarks, with weak isospin acting three left-handed doublets and
six right-handed singlets. Note that the weak eigenstates of the quarks
differ from the physical states, which mix via the \ac{CKM}-matrix CITATION
in charged current interactions as
\begin{equation}\label{eqn:ckm_matrix}
\begin{pmatrix} d' \\
s' \\
b'  \end{pmatrix} = \begin{pmatrix} V_{ud} & V_{us} & V_{ub} \\
V_{cd} & V_{cs} & V_{cb} \\
V_{td} & V_{ts} & V_{tb} \end{pmatrix} \begin{pmatrix} d \\
s\\
b \end{pmatrix}.
\end{equation}

\subsection{The electroweak force}
\label{sec:theory_sm_ewk}
The unification of the weak and electromagnetic forces, introduced
in the 1960s by Glashow \cite{glashow-ewk}, Weinberg \cite{weinberg-ewk} and Salam \cite{salam-ewk},
is a key component of the \ac{SM}. The unification of these forces,
governed by an SU(2)$\times$U(1) symmetry, implies the presence of a charged
current. A quantum number, weak hypercharge $Y$, is introduced. Weak
hypercharge is related to weak isospin $I_{1,2,3}$ and electric charge as
\begin{equation}\label{eqn:hypercharge}
Q=I_3 + \frac{1}{2}Y.
\end{equation}
We then have the three weak isospin fields, $W_{\mu}^{i}$, and the
weak hypercharge field $Y_{\mu}$, which mix to form the physical \Pphoton,
\PZ and $\PW^{\pm}$ states as
\begin{align}\label{eqn:ewk_propagators}
\PW^{\pm} &= \frac{1}{\sqrt{2}}(W_{\mu}^1 \mp i W_{\mu}^2),\\
A_{\mu} &= W_{\mu}^3\sin{\theta_W} + Y_{\mu}\cos{\theta_W},\\
Z_{\mu} &= W_{\mu}^3\cos{\theta_W} - Y_{\mu}\sin{\theta_W}.
\end{align}
In these equations $A_{\mu}$ is the photon field and $Z_{\mu}$ the \PZ field.
The weak mixing angle $\theta_W$ is related to the weak (g) and electromagnetic (g')
coupling constants as
\begin{equation}\label{eqn:thetaw}
g\sin{\theta_W} = g'\cos{\theta_W}
\end{equation}

The gauge invariance of the Lagrangian would be broken
by the addition of mass terms. For the photon this is fine, as we know it
is massless, but it is known that the \PW and \PZ bosons, as well as fermions, 
are massive. This means electroweak symmetry must be broken. In the \ac{SM}
this is achieved via the Higgs mechanism.

\subsection{The Higgs mechanism}
\label{sec:theory_sm_higgsmech}
The masses of the vector bosons are generated via the
Higgs mechanism, proposed in the 1960s by Englert and Brout \cite{englertbrout}

@@

On the fourth of July 2012 the ATLAS and CMS collaborations
announced the discovery of a boson with a mass of around 125 GeV \cite{HDiscoveryATLAS,HDiscoveryCMS}.
The observations were based on excesses in the search for $\PHiggslight\rightarrow\gamma\gamma$ and $\PHiggslight\rightarrow \PZ\PZ$.
More data were collected and analysed during the remainder of 2012, and subsequent studies 
grew the confidence in this boson being compatible with the standard model Higgs boson. The ATLAS and CMS combined
mass measurement using the full dataset of Run 1 of the \ac{LHC} 
found \mh = $125.09 \pm 0.21 \text{ (stat) } \pm 0.11 \text{ (syst) }$ GeV \cite{MassComb}.
The combined ATLAS and CMS production- and decay rate measurement, also using the full dataset of \ac{LHC} Run 1,
shows very good agreement with the \ac{SM} predictions \cite{CouplComb}. In addition, through
this combination the $\PHiggslight \rightarrow \Pgt\Pgt$ decay was observed with a significance of 5.5$\sigma$, while
the individual experiments did not reach a significance upwards of 5$\sigma$ in this channel during Run 1.
Despite the good agreement with the \ac{SM}, some discrepancies do remain, 
and so the measurements of \ac{SM} Higgs boson
properties are certainly not finished yet.

@@

During Run 2 of the LHC, standard model Higgs boson measurements, and searches for the 
standard model Higgs boson in decay channels not previously established, have 
already been performed. The decay in to $\gamma\gamma$ has been re-established \cite{CMSHgamgam2016,ATLASHgamgam2016},
as has the decay in to $ZZ\rightarrow 4\ell$ \cite{CMSHZZ2016,ATLASHZZ2016}. In addition, measurements
of $H\rightarrow WW$ are under way \cite{CMSHWW2016,ATLASHWW2016}. Establishment of the decay of 
$H\rightarrow b\bar{b}$ \cite{CMSVBFHbb2016,ATLASVHbb2016} and of $H\rightarrow \mu\mu$ \cite{ATLASHmm2016} 
is still to be achieved.
Finally, searches for ttH production, important to establish the top-Higgs coupling, have also been carried 
out \cite{CMSttH2016,CMSttHmultilep2016,ATLASttHbb2016,ATLASttHmultilep2016}. As the Run 2 dataset
keeps growing, more such measurements will be made to shed more light on the standard model Higgs boson.

\section{Beyond the standard model}
\label{sec:theory_BSM}
The \ac{SM} has been successfully tested to high accuraccy \cite{pdg-2014}. However,
some issues remain that cannot be addressed by the \ac{SM} alone \cite{griffiths}.
For example, it does not provide a candidate for dark matter. 
Additionally, the energy dependence of the running coupling constants
do not converge the GUT scale, and the force of gravity does not
appear in the \ac{SM}, no quantum theory can be formulated for it.

These issues aside, one of the most pressing issues regarding
the Higgs sector of the \ac{SM} is the hierarcy problem.
The \ac{SM}
is accepted to be an effective field theory that describes
the elementary particles and their interactions well up to an energy scale $\Lambda$.
This is the energy scale at which new physics must enter.
We know that $\Lambda \leq \mathcal{O}(10^{19})$, the Planck scale, as quantum 
gravitational effects start to become important in that region. $\Lambda$ enters
the corrections due to fermion and boson loops to the Higgs boson mass quadratically \cite{MSSM-carena-haber}:
\begin{equation}\label{eqn:mh_hierarchy}
m_{h_{\text{SM}}}^2  = (m_h^2)_0 + \mathcal{O}(\Lambda^2).
\end{equation}
Thus assuming that there is no new physics all the way up to
the Planck scale the observation \mh=125 GeV would only be compatible with $\Lambda$ of order $10^{19}$ GeV
if there was extreme fine-tuning of the bare Higgs boson mass $(m_h^2)_0$.

Many \acf{BSM} theories have been developed
that can to address the hierarchy problem and some of the other issues 
discussed. One of the most
popular of such theories is \acf{SUSY} \cite{SUSY-primer}, which postulates
that there is a symmetry between bosons and fermions. Every fermionic
\ac{SM} particle has a bosonic superpartner (named `s'+name of fermion, e.g.
sbottom, selectron,...), and every bosonic \ac{SM} particle
has a fermionic superpartner (named boson name + `ino', e.g. higgsino, Wino,...).

If this symmetry were unbroken the \ac{SUSY} particles must
have the same mass as their \ac{SM} partners. However, if that had 
been the case such particles would have been detected a long time ago. The 
only possibility is then that \ac{SUSY} is a broken symmetry and the superpartners
are heavier than their \ac{SM} equivalents. It is important to note
that the fermion and boson loops contribute to the Higgs boson
mass corrections with opposite sign, and so, if \ac{SUSY}
was an exact symmetry their contributions to the Higgs boson mass
would cancel. Due to 
symmetry breaking the contributions of \ac{SM} particles 
and their supersymmetric partners do not completely cancel. If
the \ac{SUSY} breaking scale, where new particles should
be found, is much larger than a few TeV further fine-tuning of 
the bare Higgs boson mass would be required \cite{MSSM-carena-haber,SUSY-primer}.
Apart from solving the hierarchy problem, \ac{SUSY} addresses some
of the other aforementioned issues. The lightest \ac{SUSY} particle
would be a candidate for dark matter if it were stable \cite{SUSY-primer}. On top of that
assuming \ac{SUSY} means the electroweak and strong coupling
constants intersect at a common energy scale of $\mathcal{O}(10^{16} \text{ GeV })$ \cite{GUT-LEP}.

The simplest supersymmetric extension of the \ac{SM}, the \ac{MSSM} \cite{SUSY-primer}, only adds the minimum
number of particles and fields required to formulate a supersymmetric theory.
%And conserves R-parity, see section 6.2 of the SUSY primer

\subsection{The Higgs sector of the \ac{MSSM}}
\label{sec:theory_MSSM_H}
At least two Higgs doublets are required in the
Higgs sector of the \ac{MSSM} due to the supersymmetric
background of the theory \cite{MSSM-carena-haber}. Two complex Higgs doublets are added,
\begin{equation}\label{eqn:mssm_higgsdoublets}
\phi_d = \begin{pmatrix} \phi_d^0 \\
\phi_d^- \end{pmatrix} \text{ and } \phi_u = \begin{pmatrix} \phi_u^+ \\
\phi_u^0 \end{pmatrix}
\end{equation}
Note that $\phi_d^0$ couples exclusively to down-type fermions, and $\phi_u^0$ couples
exclusively to up-type fermions.
This leads to potential terms in the MSSM Lagrangian of the form:
\begin{equation}\label{eqn:mssm_lagrangian_potential}
V = \mu(\phi_u^+\phi_d^- - \phi_u^0\phi_d^0),
\end{equation}
with $\mu$ a mass parameter, equivalent to the \ac{SM} Higgs mass parameter.
This provides electroweak symmetry breaking as in the \ac{SM} case and
minimising this potential gives,
\begin{equation}\label{eqn:mssm_minimpot}
\langle 0|\phi_d| 0 \rangle = \begin{pmatrix}v_d\\
0 \end{pmatrix} \text{ and} \langle 0 |\phi_d|\rangle 0 = \begin{pmatrix} 0\\
v_u \end{pmatrix}
\end{equation}
Using this we define
\begin{equation}\label{eqn:tanb_def}
\tan{\beta} \equiv \frac{v_u}{v_d}
\end{equation}
Of the eight degrees of freedom due to the introduction of two complex
doublets, three become longitudinal states of the $\PW^{\pm}$ and \PZ bosons.
The remaining 5 degrees of freedom lead to five physical Higgs bosons, a charged
Higgs boson pair $\PHiggs^{\pm}$, the neutral pseudoscalar \PHiggsps
and the neutral scalars h and H. These are defined in terms
of \tanb~and a mixing angle $\alpha$ which arises from diagonalising
the neutral scalar Higgs squared-mass matrix, see equation \ref{eqn:treelevel_mass}. The five bosons become:
\begin{align}\label{eqn:MSSMHiggsMixing}
&\PHiggs^+ = \phi_u^+\cos{\beta} + \phi_d^{-\dagger}\sin{\beta},\\
&\PHiggs^- = \phi_u^{+\dagger}\cos{\beta} + \phi_d^{-}\sin{\beta},\\
&\PHiggsps = \sqrt{2}(\text{Im}\phi_d^0\sin{\beta} + \text{Im}\phi_u^0\cos{\beta}),\\
&\PHiggslight = -(\sqrt{2}\text{Re}\phi_d^0 - v_d)\sin{\alpha} + (\sqrt{s}\text{Re}\phi+u^0 -v_u)\cos{\alpha}\\
&\PHiggs = (\sqrt{2}\text{Re}\phi_d^0-v_d)\cos{\alpha}+(\sqrt{2}\text{Re}\phi_u^0-v_u)\sin{\alpha}
\end{align}
As the self-interactions of the Higgs fields are not independent parameters
but are functions of the electroweak gauge coupling constants, at tree
level the MSSM Higgs sector parameters are determined by two free parameters, \tanb~and
one of the Higgs boson masses, conventionally chosen as \mA.
Using this the masses of the five Higgs states are found as:
\begin{equation}\label{mssm_chargedhigss_mass}
m_{\PHiggs^{\pm}}^2 = m_{\PHiggsps}^2+m_{\PW}^2,
\end{equation}
while the neutral scalar \PHiggslight and \PHiggs are eigenstates of the tree-level
squared-mass matrix:
\begin{equation}\label{eqn:treelevel_mass}
\mathcal{M}_{\text{tree}}^2 = \begin{pmatrix} 
m_{A}^2\sin{\beta}^2 + m_{Z}^2\cos{\beta}^2 & -(m_{A}^2+m_{Z}^2)\sin{\beta}\cos{\beta}\\
-(m_{A}^2+m_{Z}^2)\sin{\beta}\cos{\beta} & m_{A}^2\cos{\beta}^2+m_{Z}^2\sin{\beta}^2 \end{pmatrix}.
\end{equation}
This leads to the masses of \PHiggslight and \PHiggs as eigenvalue of $\mathcal{M}_{\text{tree}}^2$,
\begin{equation}\label{eqn:scalarmass}
m_{\PHiggs,\PHiggslight}^2 = \frac{1}{2}(m_{A}^2+m_{Z}^2 \pm \sqrt{(m_A^2+m_Z^2)^2-4m_Z^2m_A^2\cos{2\beta}^2}).
\end{equation}
A consequence of this is a tree-level upper bound to the mass of the light Higgs
boson,
\begin{equation}\label{eqn:mh_upper}
m_{h} \leq m_{Z},
\end{equation}
and a constraing on $\alpha$,
\begin{equation}\label{eqn:alpha_constraint}
\cos{(\beta-\alpha)}^2 = \frac{m_h^2(m_Z^2-m_h^2)}{m_A^2(m_H^2-m_h^2)}.
\end{equation}

@@

In Run-2 of the \ac{LHC} searches for \AHtotautau, setting more stringent limits than those shown in \ref{fig:bsm_summary},
have been performed in \ac{CMS}. The results of these searches will be presented in chapter \ref{chap:mssm}. 
Similar searches have been performed by \acs{ATLAS} \cite{ATLASMSSMtautau2016}. Neutral BSM Higgs bosons
are being searched for in other channels too, with some results for decays into \ttbar \cite{ATLASHttbar}, 
ZZ \cite{CMSHZZ2016,ATLASHZZ2016}, and WW \cite{ATLASHeavyHWW} already public.
In addition, searches for charged
Higgs bosons \cite{ATLASHplustaunu,ATLASHplustb,CMSHplustaunu} and
di-Higgs searches \cite{ATLASHbbgamgam,ATLASHgamgamWW,ATLASHhhbbbb,CMSbbgamgam,CMSHbbtautau,CMSHbbWW}, both in 
various final states, have been performed. The interest in these searches will remain, and so
as more data are collected during Run 2 more of such searches will be performed.
